Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
wording

The \textit{scikit-learn} project~\citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself, the
project is a library of machine learning tools  rather than  a novel domain-
specific programming language. Among other things, the library includes
classical learning algorithms, model selection tools and preprocessing
procedures. From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the Numpy and
SciPy~\citep{vanderwalt2011, varoquaux2013scipy} libraries. As such, \textit
{scikit-learn} is intended to be used within Python scripts and requires some
Python programming knowledge. At the time, it offers no command line or
graphical user interface.
% XXX Gael: maybe we should say that it augments a general purpose
% language with machine learning concepts, like numpy augments it with
% array-computing concepts.

>>>>

The \textit{scikit-learn} project~\citep{pedregosa2011} is an open source
machine learning library for the Python programming language. The ambition of
the project is to provide efficient and well-established machine learning tools
within a programming environment that is accessible to non-machine learning
experts and reusable in various scientific areas. In itself the project isn't 
a novel domain-specific language, but library that provides machine
learning idioms to a general-purpose high-level language. Among other things,
it includes classical learning algorithms, model selection tools and
preprocessing
procedures. From its core, the library has been designed to tie in with the set
of numeric and scientific packages centered around the Numpy and
SciPy~\citep{vanderwalt2011, varoquaux2013scipy} libraries. As such, \textit
{scikit-learn} is intended to be used within Python scripts and requires some
Python programming knowledge. At the time, it offers no command line or
graphical user interface.
% XXX Gael: maybe we should say that it augments a general purpose
% language with machine learning concepts, like numpy augments it with
% array-computing concepts.
